RUPEE: A fast and accurate purely geometric protein structure search

### 2019-01-10 docs/rupee_2.tex
ce alignments and filter sizes

In fast mode, the top 8,000 matches from the min-hashing and LSH initial filtering are obtained.
For each match, we calculate the exact denominator in the definition of Jaccard similarity from the original shingle sequences of the structures.
As for the numerator, instead of using the total number of matched shingles, we use the length of the longest common subsequence (LCS) of the shingle sequences for each match. 
This LCS adjustment to the Jaccard similarity enforces the constraint that all valid shingles matches must appear in order along the length of each structure. 
The final step of fast mode is to sort the matches based on the adjusted scores and return the results.

Top-aligned is an additional step following fast mode. 
First, unoptimized CE alignments are performed on the top 2,000 matches obtained from fast mode. 
Then optimized CE alignments are performed on the top 400 matches and these are finally returned sorted either by RMSD or TM-Score. 
Top-aligned is a simple layer following fast mode that establishes RUPEE fast mode as an effective filtering method that contains in its top 2,000 results enough good matches to compete with the best available structure searches.

@@

The trend of increasing response times for RUPEE top-aligned is a direct result of the pairwise structure comparisons that are performed on the top 2,000 results provided by RUPEE fast mode.

>>>>

In fast mode, the top 8000 matches from the min-hashing and LSH initial filtering are obtained.
For each match, we adjust the Jaccard similarity to account for matched shingles that are out of sequence order. 
For this adjustment, we calculate the exact denominator in the definition of Jaccard similarity from the original shingle sequences of the structures.
As for the numerator, instead of using the total number of matched shingles, we use the length of the longest common subsequence (LCS) of the shingle sequences for each match. 
This LCS adjustment to the Jaccard similarity enforces the constraint that all valid shingles matches must appear in order along the length of each structure. 
The final step of fast mode is to sort the matches based on the adjusted Jaccard similarity scores and return the results.

Top-aligned is an additional step following fast mode that uses CE to identify the best pairwise alignments among the top 2000 alignments from fast mode.
First, we perform unoptimized CE alignments on the top 2000 matches obtained from fast mode. 
Then, we perform optimized CE alignments on the top 400 matches based on the unoptimized alignments and these results are finally returned sorted either by RMSD or TM-Score. 
We limit the optimized CE alignments to the top 400 matches because for CE pairwise alignments, finding an optimized alignment through the use of dynamic programming is an additional time-intensive step.
The details of the difference between unoptimized and optimized CE alignments can be found in \cite{Shindyalov1998}.

Top-aligned is a simple layer following fast mode that establishes RUPEE fast mode as an effective filtering method that contains in its top 2000 results enough good matches to compete with the best available structure searches.
The filter sizes of 8000, 2000, and 400 for fast mode, unoptimized CE alignments, and optimized CE alignments, respectively, have been chosen based on quality of results and speed. 
We have found that increasing the size of each of these filters results in only marginal improvements in the quality of results. 
Given that performing pairwise alignments is the most time-consuming aspect of the RUPEE structure search, the marginal improvements gained from larger filter sizes have to be balanced against the number of pairwise alignments performed.

@@

The trend of increasing response times for RUPEE top-aligned is a direct result of the pairwise structure comparisons that are performed on the top 2000 results provided by RUPEE fast mode.
